Detection and partial characterisation of stellar multiplicity with Gaia

### 2018-06-30 article/ms.tex
things

\title{Detection and characterisation of stellar multiplicity with Gaia}

@@

\begin{figure*}
	\includegraphics[width=1.0\textwidth]{../figures/todo.png}
    \caption{Fraction of \Gaia\ sources with reported radial velocities
		     as a function of source properties. Within the adopted source
		     parameter ranges (gray; see Section \ref{sec:sb2_methods})
		     the radial velocity completeness is approximately flat.
		     We flag sources within this range that do not have reported 
		     radial velocities to be candidate SB2 systems.}
    \label{fig:radial_velocity_completeness}
\end{figure*}

@@

% Figure: radial velocity completeness as a function of pertinent properties
% 		  with the range that we have said is "fully complete"

% Figure: h-r diagram of SB2 binary fraction

@@

% Figure: radial veloci

@@

\todo{selecting similar sources}

\todo{fitting the two-component model}

\todo{evaluating probability}

\todo{calculating source properties}

In principle for well-sampled circular orbits this model would allow us to
identify binary star systems with orbital periods at least up to twice the observing
span in the second \Gaia\ data release ($\approx$21 months observing span; 
allowing for well-characterised detections for systems with orbital periods up to $\approx$44 months).

For higher-order star systems with longer periods, we can still find that a
stellar multiple system is more likely than a single star scenario, but our
estimate of the orbital properties (e.g., the semi-amplitude $K$) will be biased
to lower values because we have not fully sampled half of the orbital period.
At even longer orbital periods, or for stellar multiples with mass ratios that
produce a small velocity semi-amplitude $K$, under our assumptions these systems 
may be classified as single-star systems because the intrinsic radial velocity variation is within the expected 
variations for single stars of a similar apparent magnitude and colour. We 
revisit this issue in Section \ref{sec:sb_limits}, where we explicitly define 
the probability that a \Gaia\ source is a SB1-type system $p(\textrm{SB1}|y)$ 
within defined limits of orbital period (and other orbital and source parameters). 
Outside of this parameter range, we are insensitive to distinguishing single-star 
systems from higher-order SB1-type systems.

% Model fitting.

% Figure: fitting the radial velocity variance as a function of stellar properties.

% Figures: Binarity as a function of source properties.

% Figure: h-r diagram of SB1 binary fraction

% Figure: histogram of binaries as a fucntion of the Rv excess

ty fraction as a function of galactic latitude and
% 		  longitude

@@

\begin{figure*}
	\includegraphics[width=1.0\textwidth]{../figures/todo.png}
    \caption{Source radial velocity variance shown with respect to flux in
    the \Gaia\ BP, G, and RP bands. The source radial velocity variance 
    most closely follows the RP flux as it is closer to the \Gaia\ RVS
    band.}
\end{figure*}

\begin{figure}
	\includegraphics[width=0.5\textwidth]{../figures/todo.png}
    \caption{Source mean \Gaia\ RP flux and radial velocity variance.
    Points are represented by their mean $BP-RP$ color, confirming that
    there is some color dependency on the source radial velocity variance.}
    \label{fig:rp-flux-color}
\end{figure}

\begin{figure}
	\includegraphics[width=0.5\textwidth]{../figures/todo.png}
    \caption{Mixture model fitted.}
    \label{fig:mixture-model}
\end{figure}

\begin{figure}
	\includegraphics[width=0.5\textwidth]{../figures/todo.png}
    \caption{Detected binary fraction as a function of the mean RP flux
    (top panels), the $BP-RP$ color (second panels), the number of 
    radial velocity transits (third panels), and the inferred temperature
    (bottom panels). No trend is observed with mean RP flux or the number 
    of radial velocity transits. However, our model finds bluer (hotter)
    stars are more likely to be binaries, despite including color as a
    dependency in our model.}
    \label{fig:binary-fraction-wrt-params}
\end{figure}

\begin{itemize}

\item CALIBRATION SAMPLE (including ADQL query)

\item Fitting the model:

\item Comparisons of residuals with other stellar properties.

\item What is the RV error that Gaia can measure in a single epoch for a given magnitude vs colour, etc.

\item What are the distributions of orbital parameters of binary systems that we would be able to detect?

\item Calculating a probability of binarity for every star, taking the non-measurements into account!

\item Completeness cuts,.... selection effects?

\end{itemize}

@@

\begin{itemize}

\item Binary fraction in the spaces that we were fitting: rp flux, colour, etc, just showing the transition of  probabilities

\item Binary fraction as a function of fitting properties, and other stellar properties from Gaia

\item Binarity across the H-R diagram

\item Binarity with metallicity 
\end{itemize}

@@

@@

\begin{itemize}
    \item \todo{binarity with metallicity}
    \item \todo{binarity across the H-R diagram}
    \item \todo{binarity in clusters vs the field?}
    \item \todo{binarity among extremely metal-poor stars?}
\end{itemize}

@@

>>>>

\title{Detection and partial characterisation of stellar multiplicity with Gaia}

@@

\begin{figure*}
	\includegraphics[width=1.0\textwidth]{../figures/todo.png}
    \caption{Fraction of \Gaia\ sources with reported radial velocities
		     as a function of source properties. Within the adopted source
		     parameter ranges (gray; see Section \ref{sec:sb2_methods})
		     the radial velocity completeness is approximately flat.
		     We flag sources within this range that do not have reported 
		     radial velocities to be candidate SB2 systems.}
    \label{fig:sb2_rvs_completeness}
\end{figure*}

@@

\begin{figure*}
	\includegraphics[width=1.0\textwidth,height=3.0in]{../figures/todo.png}
    \caption{Hertzsprung-Russell diagram of X \Gaia\ sources that are in the
    		 ranges specified in Equation \ref{eq:rvs_parameter_ranges} (gray).
		 	 Overlaid in colour we show the SB2 candidates we deduce by the
			 absence of reported radial velocity.}
    \label{fig:sb2_hrd}
\end{figure*}

@@

@@

\todo{Bayes factors for each dimension?}

\todo{source properties: semi-amplitude (easy)}

\todo{Can we recover period and eccentricity using The Joker?}

%For higher-order star systems with longer periods, we can still find that a
%stellar multiple system is more likely than a single star scenario, but our
%estimate of the orbital properties (e.g., the semi-amplitude $K$) will be biased
%to lower values because we have not fully sampled half of the orbital period.
%At even longer orbital periods, or for stellar multiples with mass ratios that
%produce a small velocity semi-amplitude $K$, under our assumptions these systems 
%may be classified as single-star systems because the intrinsic radial velocity variation is within the expected 
%variations for single stars of a similar apparent magnitude and colour. We 
%revisit this issue in Section \ref{sec:sb_limits}, where we explicitly define 
%the probability that a \Gaia\ source is a SB1-type system $p(\textrm{SB1}|y)$ 
%within defined limits of orbital period (and other orbital and source parameters). 
%Outside of this parameter range, we are insensitive to distinguishing single-star 
%systems from higher-order SB1-type systems.

@@

@@

@@

\begin{itemize}
	\item \todo{Binary fraction in the spaces that we were fitting: rp flux, colour, etc, just showing the transition of  probabilities}
	\item \todo{Binary fraction as a function of fitting properties (e.g., colour, absolute RP mag, apparent RP mag)}
	\item \todo{Binarity across the H-R diagram}
	\item \todo{What are the distributions of orbital parameters of binary systems that we would be able to detect?}
\end{itemize}

@@

\begin{itemize}
	\item \todo{Binarity with metallicity }
    \item \todo{binarity in clusters vs the field?}
    \item \todo{binarity among extremely metal-poor stars?}
\end{itemize}

@@

\appendix
\section{Reproducibility}
This project was developed in a \texttt{git} repository that is publicly
accessible at \url{https://github.com/andycasey/velociraptor}. The repository
includes notebooks that detail our work, \LaTeX\ to compile this manuscript, 
and scripts to reproduce our analysis in its entirety. Reproducing this work in 
full will require at least \todo{X}\,Gb of disk space and \todo{Y}\,compute hours.
To reproduce this work (including data retrieval, analysis, production of figures,
and manuscript compilation) use the \todo{following commands on a modern terminal}:

\section{Relevant Astronomical Data Query Language (ADQL) queries}
\todo{Include relevant ADQL queries}

\section{Radial velocity completeness as a function of \Gaia\ source properties}
\todo{Figures}
